---
title: "Getting Started with R"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include = FALSE, echo = TRUE}

load("~/Dropbox/PSCI 2075/Data/New Data/Art_and_Practice.RData")

libraries()

```

## A Little Practice  

Produce a few graphs to see exactly how RStudio works.  Above, in the first chunk, the data are loaded and the *libaries()* command has been executed.  Since we know where the data are, we can start playing around.  Begin by making a histogram and a scatter plot.

A histogram provides a nice picture of a variable's distribution (there will be more on that later).  It indicates the range of a variable and where most of the cases lie in that range.  Below is a simple code chunk that produces a histogram for a variable in the *states* data set called *hsdiploma*, the percentage of the state's adult population who have a high-school level education.

```{r}

hist(states$hsdiploma)

```


Below is the code chunk to create a scatter plot of the two variables *murderrate* and *hsdiploma* from the *states* data set, using the most basic form of a scatter plot.

```{r}

plot(states$hsdiploma, states$murderrate)

```

The scatter plot should appear just under the chunk and just before this paragraph.  You can change the settings so that the graphs you produce will appear in the bottom-right quadrant for closer inspection.  To do that, go to the gear icon at the top of this window and choose *Chunk Output in Console*.  Now that we've loaded the data, run *libraries()* and produced a few plots, let's *knit* the document.

Once you've checked to make sure all of the code chunks in the R Markdown file run properly, choose the small arrow by the *Knit* icon at the top of this window and choose either *word* or *html*.  RStudio will begin generating a document (progress is reported in the Console window).  If done correctly (usually the test is that all code chunks are running properly), you should have a nice-looking html or word document.

Finally, let's do a simple example that shows how we can define an object and then execute a function on that object. Let's use the example presented earlier in the chapter where we defined the object called 'myobject' as a list of 12 numbers. Once we've defined 'myobject', we can take the function 'hist()' and insert 'myobject' in the parentheses to make a histogram of those 12 numbers we typed in.

```{r}

myobject <- c(1,1,1,1,3,4,5,5,5,5,6,6)

hist(myobject, main = "Figure 1-8: Histogram of 12 Numbers")

```


